Analyzing DECREASE trials to estimate evidence of data manipulation

### 2017-10-18 submission/manuscript.Rmd
Minor changes and data for interactive figure

---
title: "Analyzing DECREASE trials to estimate evidence of data manipulation"
author: "[Chris H. J. Hartgerink](https://orcid.org/0000-0003-1050-6809), E. M. Kemper, [Markus W. Hollman](https://orcid.org/0000-0001-8248-0244), [Gerben ter Riet](https://orcid.org/0000-0002-2231-7637)"
date: '`r format(Sys.time(), "%d %B, %Y")`'
output:
  pdf_document:
    fig_caption: yes
    keep_tex: yes
  html_document: default
  word_document: default
csl: ../bibliography/ama.csl
bibliography: ../bibliography/library.bib
---

@@

All manuscript materials are available at https://github.com/chartgerink/2015poldermans and are preserved at Zenodo [@chris_hartgerink_2017_845355]. CHJH was funded by the Office of Research Integrity during part of this project (ORI; ORIIR160019).

@@

```{r, echo = FALSE}
pdf(sprintf('%sfigures/fig2.pdf', x12), width = 8, height = 6)
tau2 <- seq(0, .5, .01)

@@

par(mar = c(4, 4, 1, 0))
plot(tau2, prob_sens_t, type = 'l', xlab = TeX('$\\tau^2$'),
     ylab = 'p-value', bty = 'n')
# points(x = tau2[c(26, 44)], y = prob_sens_t[c(26, 44)])
# text(x = tau2[c(26, 44)],
#      y = prob_sens_t[c(26, 44)] + .003,
#      labels = c(TeX('$\\tau^2=.25$'), TeX('$\\tau^2=.43$')),
#      cex = .8)
invisible(dev.off())
```
```{r figure 2, fig.cap = 'Sensitivity analyses for the p-value that indicates the probability of observing the results from the DECREASE studies, or more extreme results, based on the estimated true effect (non-DECREASE trials) and the accompanying variance estimate.', out.width = '80%', fig.asp = .5, fig.align = 'center', echo = FALSE}
knitr::include_graphics(sprintf("%sfigures/fig2.pdf", x12))
fignr <- fignr + 1
```

@@

We applied the inversion method to estimate the number of manipulated data points in the DECREASE trials [@casella2002]. We assumed that if data are manipulated, each data point is manipulated in the same way and to the same extent. The inversion method iteratively hypothesizes that *X* out of *N* data points were manipulated (i.e., $X={0, 1, ..., N}$), assuming they were manipulated in the same way. For each combination of *X* and trial, we simulated `r iterations` datasets. Each simulated dataset contained *X* manipulated data points and *N-X* genuine data points. For each simulated dataset (exact simulation procedure in the next paragraph), we determined the likelihood of the results with 
\begin{equation}
\label{eq1}
L(\theta|\pi_{E},\pi_{C})=\pi_{E}^{n_{11}}(1-\pi_{E})^{n_{12}} \times \pi_{C}^{n_{21}}(1 - \pi_{C})^{n_{22}}
\end{equation}
where $\pi_{E}$ indicates the mortality rate in the beta-blocker condition as drawn from the meta-analytic effect distribution ($\pi_{C}$ indicates the mortality rate in the control condition). We estimated those parameters using the meta-analytic procedure described in the previous paragraph, resulting in the estimates depicted in Table `r tabnr`. The likelihood was computed under both the manipulated effect estimates (i.e., $L_{manipulated}$) and the genuine data (i.e., $L_{genuine}$). Table 4 indicates which cell sizes the various $n_{XX}$ refer to within the (simulated) data. After computing the likelihoods, we compared them to determine whether the simulated data were more likely to arise from the genuine trials ($L_{genuine}>L_{manipulated}$) or from the manipulated trials ($L_{manipulated}>L_{genuine}$). Note that comparing the likelihoods is a minor deviation from the preregistration, where we initially planned on using $p$-value comparisons ([osf.io/vnmzc](https://osf.io/vnmzc)).

@@

Based on the meta-analytic effect from 2 and the cell sizes from 3, we computed the likelihoods $L_{manipulated}$ and $L_{genuine}$ using Equation \ref{eq1}. As mentioned before, we computed $p_M$, which indicates the probability that the data are more likely under the estimates resulting from the (allegedly) manipulated data (i.e., the DECREASE trials) than under the estimates resulting from the genuine data (i.e., the non-DECREASE trials; $p_M=P(L_{manipulated}>L_{genuine})$).

@@

  res_i_uncertain_lb[j] <- which(abs(res_i_uncertain - lb) == min(abs(res_i_uncertain - lb)))[1]
  res_i_uncertain_ub[j] <- which(abs(res_i_uncertain - ub) == min(abs(res_i_uncertain - ub)))[1]

  res_i_certain_lb[j] <- which(abs(res_i_certain - lb) == min(abs(res_i_certain - lb)))[1]
  res_i_certain_ub[j] <- which(abs(res_i_certain - ub) == min(abs(res_i_certain - ub)))[1]

  res_iv_uncertain_lb[j] <- which(abs(res_iv_uncertain - lb) == min(abs(res_iv_uncertain - lb)))[1]
  res_iv_uncertain_ub[j] <- which(abs(res_iv_uncertain - ub) == min(abs(res_iv_uncertain - ub)))[1]

  res_iv_certain_lb[j] <- which(abs(res_iv_certain - lb) == min(abs(res_iv_certain - lb)))[1]
  res_iv_certain_ub[j] <- which(abs(res_iv_certain - ub) == min(abs(res_iv_certain - ub)))[1]

@@

pdf(sprintf('%sfigures/fig3.pdf', x12), width = 8, height = 6)

@@

plot(x = NA, y = NA,
     xlim = c(0,1), ylim = c(0, length(res_i_certain)),
     xlab = "Confidence in %", ylab = "Number of data points manipulated")

lines(x = seq(0, 1, .01), y = res_i_uncertain_lb)
lines(x = seq(0, 1, .01), y = res_i_uncertain_ub)
lines(x = seq(0, 1, .01), y = res_i_certain_lb, lty = 2, pch = 2, type = 'l')
lines(x = seq(0, 1, .01), y = res_i_certain_ub, lty = 2, pch = 2, type = 'l')
abline(v = .95, lty = 3)

@@

plot(x = NA, y = NA,
     xlim = c(0,1), ylim = c(0, length(res_iv_certain)),
     xlab = "Confidence in %", ylab = "",
     yaxt = 'n')

lines(x = seq(0, 1, .01), y = res_iv_uncertain_lb)
lines(x = seq(0, 1, .01), y = res_iv_uncertain_ub)
lines(x = seq(0, 1, .01), y = res_iv_certain_lb, lty = 2, pch = 2, type = 'l')
lines(x = seq(0, 1, .01), y = res_iv_certain_ub, lty = 2, pch = 2, type = 'l')
abline(v = .95, lty = 3)
invisible(dev.off())
```

@@

```{r figure 3, fig.cap = 'Inversion method results used to estimate the number of data points manipulated in the DECREASE-I and DECREASE-IV trials. The top row panels indicate $p_M$ (y-axis) for all $X$ out of $N$ manipulated data points (x-axis). The bottom row indicates the estimated interval of manipulated data points (y-axis) when varying the degree of confidence (x-axis). Dotted lines indicate the bounds for a 95 percent CI.', out.width = '80%', fig.asp = .5, fig.align = 'center', echo = FALSE}
knitr::include_graphics(sprintf("%sfigures/fig3.pdf", x12))
fignr <- fignr + 1
```

>>>>

---
title: "Analyzing DECREASE trials to estimate evidence of data manipulation"
author: '[Chris H. J. Hartgerink](https://orcid.org/0000-0003-1050-6809), E. M. Kemper,
  [Markus W. Hollman](https://orcid.org/0000-0001-8248-0244), [Gerben ter Riet](https://orcid.org/0000-0002-2231-7637)'
date: '`r format(Sys.time(), "%d %B, %Y")`'
output:
  pdf_document:
    fig_caption: yes
    keep_tex: yes
  html_document: default
  word_document: default
csl: ../bibliography/ama.csl
bibliography: ../bibliography/library.bib
---

@@

All manuscript materials are available at https://github.com/chartgerink/2015poldermans and are preserved at Zenodo ([doi.org/10.5281/zenodo.845354](https://doi.org/10.5281/zenodo.845354)). CHJH was funded by the Office of Research Integrity during part of this project (ORI; ORIIR160019).

@@

```{r, echo = FALSE}
pdf(sprintf('%sfigures/fig1.pdf', x12), width = 8, height = 6)
tau2 <- seq(0, .5, .01)

@@

par(mar = c(4, 4, 1, 0))
plot(tau2, prob_sens_t, type = 'l', xlab = TeX('$\\tau^2$'),
     ylab = 'p-value', bty = 'n')
# points(x = tau2[c(26, 44)], y = prob_sens_t[c(26, 44)])
# text(x = tau2[c(26, 44)],
#      y = prob_sens_t[c(26, 44)] + .003,
#      labels = c(TeX('$\\tau^2=.25$'), TeX('$\\tau^2=.43$')),
#      cex = .8)
invisible(dev.off())
```
```{r figure 2, fig.cap = 'Sensitivity analyses for the p-value that indicates the probability of observing the results from the DECREASE studies, or more extreme results, based on the estimated true effect (non-DECREASE trials) and the accompanying variance estimate.', out.width = '80%', fig.asp = .5, fig.align = 'center', echo = FALSE}
knitr::include_graphics(sprintf("%sfigures/fig1.pdf", x12))
fignr <- fignr + 1
```

@@

We applied the inversion method to estimate the number of manipulated data points in the DECREASE trials [@casella2002]. We assumed that if data are manipulated, each data point is manipulated in the same way and to the same extent. The inversion method iteratively hypothesizes that *X* out of *N* data points were manipulated (i.e., $X={0, 1, ..., N}$), assuming they were manipulated in the same way. For each combination of *X* and trial, we simulated `r iterations` datasets. Each simulated dataset contained *X* manipulated data points and *N-X* genuine data points. For each simulated dataset (exact simulation procedure in the next paragraph), we determined the likelihood of the results with 
$$
L(\theta|\pi_{E},\pi_{C})=\pi_{E}^{n_{11}}(1-\pi_{E})^{n_{12}} \times \pi_{C}^{n_{21}}(1 - \pi_{C})^{n_{22}}
$$
where $\pi_{E}$ indicates the mortality rate in the beta-blocker condition as drawn from the meta-analytic effect distribution ($\pi_{C}$ indicates the mortality rate in the control condition). We estimated those parameters using the meta-analytic procedure described in the previous paragraph, resulting in the estimates depicted in Table `r tabnr`. The likelihood was computed under both the manipulated effect estimates (i.e., $L_{manipulated}$) and the genuine data (i.e., $L_{genuine}$). Table 4 indicates which cell sizes the various $n_{XX}$ refer to within the (simulated) data. After computing the likelihoods, we compared them to determine whether the simulated data were more likely to arise from the genuine trials ($L_{genuine}>L_{manipulated}$) or from the manipulated trials ($L_{manipulated}>L_{genuine}$). Note that comparing the likelihoods is a minor deviation from the preregistration, where we initially planned on using $p$-value comparisons ([osf.io/vnmzc](https://osf.io/vnmzc)).

@@

Based on the meta-analytic effect from 2 and the cell sizes from 3, we computed the likelihoods $L_{manipulated}$ and $L_{genuine}$ using Equation 1. As mentioned before, we computed $p_M$, which indicates the probability that the data are more likely under the estimates resulting from the (allegedly) manipulated data (i.e., the DECREASE trials) than under the estimates resulting from the genuine data (i.e., the non-DECREASE trials; $p_M=P(L_{manipulated}>L_{genuine})$).

@@

  # MINUS ONE because R does not have zero indexing
  # AAAA
  res_i_uncertain_lb[j] <- which(abs(res_i_uncertain - lb) == min(abs(res_i_uncertain - lb)))[1] - 1
  res_i_uncertain_ub[j] <- which(abs(res_i_uncertain - ub) == min(abs(res_i_uncertain - ub)))[1] - 1

  res_i_certain_lb[j] <- which(abs(res_i_certain - lb) == min(abs(res_i_certain - lb)))[1] - 1
  res_i_certain_ub[j] <- which(abs(res_i_certain - ub) == min(abs(res_i_certain - ub)))[1] - 1

  res_iv_uncertain_lb[j] <- which(abs(res_iv_uncertain - lb) == min(abs(res_iv_uncertain - lb)))[1] - 1
  res_iv_uncertain_ub[j] <- which(abs(res_iv_uncertain - ub) == min(abs(res_iv_uncertain - ub)))[1] - 1

  res_iv_certain_lb[j] <- which(abs(res_iv_certain - lb) == min(abs(res_iv_certain - lb)))[1] - 1
  res_iv_certain_ub[j] <- which(abs(res_iv_certain - ub) == min(abs(res_iv_certain - ub)))[1] - 1

@@

N_I <- sum(bouri_data[grepl(bouri_data$study, pattern = '_I-'),c(3,5)])
N_IV <- sum(bouri_data[grepl(bouri_data$study, pattern = '_IV-'),c(3,5)])

pdf(sprintf('%sfigures/fig2.pdf', x12), width = 8, height = 6)

@@

plot(x = NA, y = NA,
     xlim = c(0,1), ylim = c(0, 100),
     xlab = "Confidence in %", ylab = "% of data points manipulated")

lines(x = seq(0, 1, .01), y = (res_i_uncertain_lb / N_I) * 100)
lines(x = seq(0, 1, .01), y = (res_i_uncertain_ub / N_I) * 100)
lines(x = seq(0, 1, .01), y = (res_i_certain_lb / N_I) * 100, lty = 2, pch = 2, type = 'l')
lines(x = seq(0, 1, .01), y = (res_i_certain_ub / N_I) * 100, lty = 2, pch = 2, type = 'l')
abline(v = .95, lty = 3)

@@

plot(x = NA, y = NA,
     xlim = c(0,1), ylim = c(0, 100),
     xlab = "Confidence in %", ylab = "",
     yaxt = 'n')

lines(x = seq(0, 1, .01), y = (res_iv_uncertain_lb / N_IV) * 100)
lines(x = seq(0, 1, .01), y = (res_iv_uncertain_ub / N_IV) * 100)
lines(x = seq(0, 1, .01), y = (res_iv_certain_lb / N_IV) * 100, lty = 2, pch = 2, type = 'l')
lines(x = seq(0, 1, .01), y = (res_iv_certain_ub / N_IV) * 100, lty = 2, pch = 2, type = 'l')
abline(v = .95, lty = 3)
invisible(dev.off())
```

@@

```{r figure 3, fig.cap = 'Inversion method results used to estimate the number of data points manipulated in the DECREASE-I and DECREASE-IV trials. The top row panels indicate $p_M$ (y-axis) for all $X$ out of $N$ manipulated data points (x-axis). The bottom row indicates the estimated interval of manipulated data points (y-axis) when varying the degree of confidence (x-axis). Dotted lines indicate the bounds for a 95 percent CI.', out.width = '80%', fig.asp = .5, fig.align = 'center', echo = FALSE}
knitr::include_graphics(sprintf("%sfigures/fig2.pdf", x12))
fignr <- fignr + 1
```

### 2017-10-18 submission/manuscript.tex
Minor changes and data for interactive figure

\setlength{\droptitle}{-2em}
  \title{Analyzing DECREASE trials to estimate evidence of data manipulation}
  \pretitle{\vspace{\droptitle}\centering\huge}
  \posttitle{\par}
  \author{\href{https://orcid.org/}{Chris H. J. Hartgerink}, E. M. Kemper,
\href{https://orcid.org/0000-0001-8248-0244}{Markus W. Hollman},
\href{https://orcid.org/0000-0002-2231-7637}{Gerben ter Riet}}
  \preauthor{\centering\large\emph}
  \postauthor{\par}
  \predate{\centering\large\emph}
  \postdate{\par}
  \date{27 July, 2017}

@@

All manuscript materials are available at
\url{https://github.com/chartgerink/2015poldermans} and are preserved at
Zenodo {[}@{]}.

@@

To statistically investigate the evidence for data manipulation in the
DECREASE studies\textsuperscript{2,3}, we took three steps. First, we
reproduced the findings from the 2014 meta-analysis by Bouri et
al.\textsuperscript{9}, which contained sufficient information to
estimate the deviation of the DECREASE trials from other published
trials on beta-blockers. We also included type of beta-blocker to
inspect whether this is predictive of the effect of beta-blockers on
perioperative mortality. Second, we evaluated the probability that the
DECREASE trials (or more extreme effects) arose from the same effect
distribution as the non-DECREASE trials, which are assumed to be the
true effect of beta-blockers on perioperative mortality in patients
undergoing non-cardiac surgery. Third, we estimated how many data points
would have to be manipulated in order to reproduce the results of the
DECREASE trials if the initial, non-manipulated results arose from the
effect estimates as obtained from the non-DECREASE trials. Considering
the committees investigating the scientific integrity of the DECREASE
trials was unable to assess this, we consider it worthwhile to
investigate this further.

@@

Based on the effect estimates for the non-DECREASE trials from Step 1,
we estimated the probability that the observed effects from the DECREASE
studies (or more extreme) occurred naturally. We assumed that the
non-DECREASE studies estimated the true effect distribution of
perioperative beta-blockade on mortality, not perturbed by publication
bias due to statistical (non)significance. Publication bias was assumed
to not be a problem because a substantial number of nonsignificant
effects are included in the dataset (9 of 11 results are
nonsignificant). Based on this effect distribution, we estimated the
veracity of the DECREASE trials separately, which is the estimated
probability of the observed data under a given true
effect\textsuperscript{19}.

@@

@@

We applied the inversion method to estimate the number of manipulated
data points in the DECREASE trials\textsuperscript{21}. We assumed that
if data are manipulated, each data point is manipulated in the same way
and to the same extent. The inversion method iteratively hypothesizes
that \emph{X} out of \emph{N} data points were manipulated (i.e.,
\(X={0, 1, ..., N}\)), assuming they were manipulated in the same way.
For each combination of \emph{X} and trial, we simulated 10000 datasets.
Each simulated dataset contained \emph{X} manipulated data points and
\emph{N-X} genuine data points. For each simulated dataset (exact
simulation procedure in the next paragraph), we determined the
likelihood of the results with

\begin{equation}
\label{eq1}
L(\theta|\pi_{E},\pi_{C})=\pi_{E}^{n_{11}}(1-\pi_{E})^{n_{12}} \times \pi_{C}^{n_{21}}(1 - \pi_{C})^{n_{22}}
\end{equation}

where \(\pi_{E}\) indicates the mortality rate in the beta-blocker
condition as drawn from the meta-analytic effect distribution
(\(\pi_{C}\) indicates the mortality rate in the control condition). We
estimated those parameters using the meta-analytic procedure described
in the previous paragraph, resulting in the estimates depicted in Table
3. The likelihood was computed under both the manipulated effect
estimates (i.e., \(L_{manipulated}\)) and the genuine data (i.e.,
\(L_{genuine}\)). Table 4 indicates which cell sizes the various
\(n_{XX}\) refer to within the (simulated) data. After computing the
likelihoods, we compared them to determine whether the simulated data
were more likely to arise from the genuine trials
(\(L_{genuine}>L_{manipulated}\)) or from the manipulated trials
(\(L_{manipulated}>L_{genuine}\)). Note that comparing the likelihoods
is a minor deviation from the preregistration, where we initially
planned on using \(p\)-value comparisons
(\href{https://osf.io/vnmzc}{osf.io/vnmzc}).

@@

Based on the meta-analytic effect from 2 and the cell sizes from 3, we
computed the likelihoods \(L_{manipulated}\) and \(L_{genuine}\) using
Equation \ref{eq1}. As mentioned before, we computed \(p_M\), which
indicates the probability that the data are more likely under the
estimates resulting from the (allegedly) manipulated data (i.e., the
DECREASE trials) than under the estimates resulting from the genuine
data (i.e., the non-DECREASE trials;
\(p_M=P(L_{manipulated}>L_{genuine})\)).

@@

{\centering \includegraphics[width=0.8\linewidth]{../figures/fig3}

@@

\begin{verbatim}
## R version 3.4.0 (2017-04-21)
## Platform: x86_64-redhat-linux-gnu (64-bit)
## Running under: Fedora 26 (Workstation Edition)
## 
## Matrix products: default
## BLAS/LAPACK: /usr/lib64/R/lib/libRblas.so
## 
## locale:
##  [1] LC_CTYPE=en_US.UTF-8       LC_NUMERIC=C              
##  [3] LC_TIME=en_US.UTF-8        LC_COLLATE=en_US.UTF-8    
##  [5] LC_MONETARY=en_US.UTF-8    LC_MESSAGES=en_US.UTF-8   
##  [7] LC_PAPER=en_US.UTF-8       LC_NAME=C                 
##  [9] LC_ADDRESS=C               LC_TELEPHONE=C            
## [11] LC_MEASUREMENT=en_US.UTF-8 LC_IDENTIFICATION=C       
## 
## attached base packages:
## [1] stats     graphics  grDevices utils     datasets  methods   base     
## 
## other attached packages:
## [1] knitr_1.16      latex2exp_0.4.0 metafor_2.0-0   Matrix_1.2-9   
## 
## loaded via a namespace (and not attached):
##  [1] Rcpp_0.12.11    lattice_0.20-35 digest_0.6.12   rprojroot_1.2  
##  [5] grid_3.4.0      nlme_3.1-131    backports_1.1.0 magrittr_1.5   
##  [9] evaluate_0.10.1 highr_0.6       stringi_1.1.5   rmarkdown_1.6  
## [13] tools_3.4.0     stringr_1.2.0   yaml_2.1.14     compiler_3.4.0 
## [17] htmltools_0.3.6
\end{verbatim}

>>>>

\setlength{\droptitle}{-2em}
  \title{Analyzing DECREASE trials to estimate evidence of data manipulation}
  \pretitle{\vspace{\droptitle}\centering\huge}
  \posttitle{\par}
  \author{\href{https://orcid.org/0000-0003-1050-6809}{Chris H. J. Hartgerink}, E.
M. Kemper, \href{https://orcid.org/0000-0001-8248-0244}{Markus W.
Hollman}, \href{https://orcid.org/0000-0002-2231-7637}{Gerben ter Riet}}
  \preauthor{\centering\large\emph}
  \postauthor{\par}
  \predate{\centering\large\emph}
  \postdate{\par}
  \date{18 October, 2017}

@@

All manuscript materials are available at
\url{https://github.com/chartgerink/2015poldermans} and are preserved at
Zenodo
(\href{https://doi.org/10.5281/zenodo.845354}{doi.org/10.5281/zenodo.845354}).
CHJH was funded by the Office of Research Integrity during part of this
project (ORI; ORIIR160019).

@@

To statistically investigate the evidence for data manipulation in the
DECREASE studies\textsuperscript{2,3}, we took three steps. First, we
reproduced the findings from the 2014 meta-analysis by Bouri et
al.\textsuperscript{9}, which contained sufficient information to
estimate the deviation of the DECREASE trials from other published
trials on beta-blockers. We also included type of beta-blocker to
inspect whether this is predictive of the effect of beta-blockers on
perioperative mortality. Second, we evaluated the probability that the
DECREASE trials (or more extreme effects) arose from the same effect
distribution as the non-DECREASE trials, which are assumed to be the
true effect of beta-blockers on perioperative mortality in patients
undergoing non-cardiac surgery. Third, we estimated how many data points
would have to be manipulated in order to reproduce the results of the
DECREASE trials if the initial, non-manipulated results arose from the
effect estimates as obtained from the non-DECREASE trials. Considering
the committees investigating the scientific integrity of the DECREASE
trials were unable to assess this, we consider it worthwhile to
investigate this further.

@@

Based on the effect estimates for the non-DECREASE trials from Step 1,
we estimated the probability that the observed effects from the DECREASE
studies (or more extreme) occurred naturally. We assumed that the
non-DECREASE studies estimated the true effect distribution of
perioperative beta-blockade on mortality, not perturbed by publication
bias due to statistical (non)significance. Publication bias was assumed
to not be a problem because a substantial number of nonsignificant
effects are included in the dataset (9 of 11 results are
nonsignificant). Based on this effect distribution, we estimated the
veracity of the DECREASE trials separately, which is the estimated
probability of the observed data (or more extreme) under a given true
effect\textsuperscript{19}.

@@

{\centering \includegraphics[width=0.8\linewidth]{../figures/fig1}

@@

We applied the inversion method to estimate the number of manipulated
data points in the DECREASE trials\textsuperscript{21}. We assumed that
if data are manipulated, each data point is manipulated in the same way
and to the same extent. The inversion method iteratively hypothesizes
that \emph{X} out of \emph{N} data points were manipulated (i.e.,
\(X={0, 1, ..., N}\)), assuming they were manipulated in the same way.
For each combination of \emph{X} and trial, we simulated 10000 datasets.
Each simulated dataset contained \emph{X} manipulated data points and
\emph{N-X} genuine data points. For each simulated dataset (exact
simulation procedure in the next paragraph), we determined the
likelihood of the results with \[
L(\theta|\pi_{E},\pi_{C})=\pi_{E}^{n_{11}}(1-\pi_{E})^{n_{12}} \times \pi_{C}^{n_{21}}(1 - \pi_{C})^{n_{22}}
\] where \(\pi_{E}\) indicates the mortality rate in the beta-blocker
condition as drawn from the meta-analytic effect distribution
(\(\pi_{C}\) indicates the mortality rate in the control condition). We
estimated those parameters using the meta-analytic procedure described
in the previous paragraph, resulting in the estimates depicted in Table
3. The likelihood was computed under both the manipulated effect
estimates (i.e., \(L_{manipulated}\)) and the genuine data (i.e.,
\(L_{genuine}\)). Table 4 indicates which cell sizes the various
\(n_{XX}\) refer to within the (simulated) data. After computing the
likelihoods, we compared them to determine whether the simulated data
were more likely to arise from the genuine trials
(\(L_{genuine}>L_{manipulated}\)) or from the manipulated trials
(\(L_{manipulated}>L_{genuine}\)). Note that comparing the likelihoods
is a minor deviation from the preregistration, where we initially
planned on using \(p\)-value comparisons
(\href{https://osf.io/vnmzc}{osf.io/vnmzc}).

@@

Based on the meta-analytic effect from 2 and the cell sizes from 3, we
computed the likelihoods \(L_{manipulated}\) and \(L_{genuine}\) using
Equation 1. As mentioned before, we computed \(p_M\), which indicates
the probability that the data are more likely under the estimates
resulting from the (allegedly) manipulated data (i.e., the DECREASE
trials) than under the estimates resulting from the genuine data (i.e.,
the non-DECREASE trials; \(p_M=P(L_{manipulated}>L_{genuine})\)).

@@

@@

\begin{verbatim}
## R version 3.4.1 (2017-06-30)
## Platform: x86_64-redhat-linux-gnu (64-bit)
## Running under: Fedora 26 (Workstation Edition)
## 
## Matrix products: default
## BLAS/LAPACK: /usr/lib64/R/lib/libRblas.so
## 
## locale:
##  [1] LC_CTYPE=en_US.UTF-8       LC_NUMERIC=C              
##  [3] LC_TIME=en_US.UTF-8        LC_COLLATE=en_US.UTF-8    
##  [5] LC_MONETARY=en_US.UTF-8    LC_MESSAGES=en_US.UTF-8   
##  [7] LC_PAPER=en_US.UTF-8       LC_NAME=C                 
##  [9] LC_ADDRESS=C               LC_TELEPHONE=C            
## [11] LC_MEASUREMENT=en_US.UTF-8 LC_IDENTIFICATION=C       
## 
## attached base packages:
## [1] stats     graphics  grDevices utils     datasets  methods   base     
## 
## other attached packages:
## [1] knitr_1.17      latex2exp_0.4.0 metafor_2.0-0   Matrix_1.2-10  
## 
## loaded via a namespace (and not attached):
##  [1] Rcpp_0.12.13    lattice_0.20-35 digest_0.6.12   rprojroot_1.2  
##  [5] grid_3.4.1      nlme_3.1-131    backports_1.1.1 magrittr_1.5   
##  [9] evaluate_0.10.1 highr_0.6       stringi_1.1.5   rmarkdown_1.6  
## [13] tools_3.4.1     stringr_1.2.0   yaml_2.1.14     compiler_3.4.1 
## [17] htmltools_0.3.6
\end{verbatim}
